Live Functional Programming with Typed Holes

### 2018-02-08 intro.tex
draft of an abstract (probably a bit too long and meandering/unclear, but its a start)
some thoughts to add to intro, somewhere

% !TEX root = hazelnut-dynamics.tex
\newcommand{\introSec}{Introduction}
\section{\protect\introSec}
\label{sec:intro}
\cy{intro from LIVE 2017 paper is below}

@@

>>>>

% !TEX root = hazelnut-dynamics.tex
\newcommand{\introSec}{Introduction}
\section{\protect\introSec} % don't like the all-caps thing that the template does, so protecting it from that
\label{sec:intro}
\cy{intro from LIVE 2017 paper is below}

@@

\matt{below are misc points that may be worth mentioning in section 1
  (somehow, somewhere), and weaving into the continuation of the story
  above:}

Type holes vs expression holes:

The dynamics of type holes is gradual typing, including run-time cast
insertion and execution.
%
The dynamics of expression holes consists of defining
\emph{indeterminate} expressions, as placeholders for subterms that
traditionally would be deemed ``stuck'' .

In live programming, we expect that programs will generally have holes
in both terms and types (CITE?); however, to understand the mechanisms
of \HazelnutLive, it is instructive to imagine situations where the
only holes or in terms, or in types.
%
  When we only use type holes (not common in live programming, AFAIK),
  we recover gradual typing and do not need indeterminate forms
  (except for cast errors, which we classify this way).  
  % 
  When we only use expression holes, we do not need type casts, or
  the other dynamic mechanisms of gradual typing.
